\documentclass[10pt, a4paper]{article} %Defines the document, we are forced to use 10pt

\usepackage{longtable}

\usepackage{fullpage} %makes the margins more reasonable for a 1 page report
\usepackage[a4paper,landscape]{geometry}

\begin{document}

\textbf{SDP Group 7 Team Performance Review 3 - \today}


\begin{longtable}{c c c p{16cm}}
    \textbf{Name} &
    \textbf{Matric No} &
    \textbf{Score} &
    \textbf{Comments}\\
    \hline
    \endfirsthead


    \textbf{Name} &
    \textbf{Matric No} &
    \textbf{Score} &
    \textbf{Comments}\\
    \hline
    \endhead

    Wiktor Brodlo &
    s0927919 &
    6&
    Because we have changed the packet format and added some more opcodes,
    I have done some maintenance on the simulator. I have spent most of my time
    debugging the Bluetooth connection, various delays across the system,
    helped fix bugs and contributed my ideas to how to improve our system.\\



    David Fraser &
    s0912336 &
    6&
    I continued to work on the interface between strategy system and the
    control system.  I assisted in the verification of the arcing mathematics
    and the search for the problem has now been shifted downstream. I also started
    the work on the presentation for the final day. Team communications have
    got better but we still had problems. Angles were still a problem but
    I acted quickly to resolved it.\\

    Radoslav Gabrovski &
    s0951580 &
    9& 
   My contributions for this milestone was getting a new interface for the
   vision system , using sliders, writing a guide so that other team members
   can use it, writing Junit tests for methods for the vision system.
   I resolved some issues with the dimensions of our robot and resolved some
   crucial bugs in arcing and verified the result.\\


    James Hulme &
    s0901522 &
    6& 
    For this milestone I have been mainly helping out trying to find and fix bugs
    in the system. I also documented the vision system code.\\

    Dale Myers &
    s0942590 &
    6&
    This week I proposed and helped implement the new control code for the
    robot. Most of the work was making the new code integrate well with the
    current system.\\


    Laurie Picken &
    s0903587 &
    7&
    Provided a versatile penalty defence system, to be used additionally for
    goal line defence when in free play. Co-wrote the control code for our
    first attempt at ball interception. Extensive testing with the robot to
    facilitate our ball prediction and ball intersection methods.\\

    Darie Picu &
    s0935756 &
    7&
    I worked in the strategy team improving the current methods so that we take
    into account the obstacles on the pitch and finished the ball predicting
    methods. I also worked in the control team trying to do a simple design for
    milestone 4 without using the arcs that we had trouble implementing.\\

    Tomas Tauber &
    s0943263 &
    6&
    I identified problems with the current Strategy code and discussed possible
    fixes with Chris, I was involved in rewriting the Control code to adapt to the
    needs of the Strategy code and fixing and investigating issues that came up
    with this new Control code, and I helped Darie, Laurie, and Dale with their
    attempts to prepare a solution for the milestone.\\

    Christopher Williams &
    s0955088 &
    6&
    I have been working on the Planning and Strategy of the robot. This
    involved me completing my work on A* and troubleshooting: to re-do the
    current A* so that it was no longer working on binary costs.\\



\end{longtable}
\textbf{Good things} - A lot of bugs were eliminated from the system and we
have narrowed the search for our control bug down to a timing issue.

\textbf{Things to improve} - There is still a bug somewhere in the control
systems which prevents us from making the robot do what we want. There are
still large areas of undocumented code which we need to finish.

\end{document}
