\documentclass[10pt, a4paper]{article} %Defines the document, we are forced to use 10pt

\usepackage{longtable}

\usepackage{fullpage} %makes the margins more reasonable for a 1 page report
\usepackage[a4paper,landscape]{geometry}

\begin{document}

\textbf{SDP Group 7 Team Performance Review 3 - \today}


\begin{longtable}{c c c p{16cm}}
    \textbf{Name} &
    \textbf{Matric No} &
    \textbf{Score} &
    \textbf{Comments}\\
    \hline
    \endfirsthead


    \textbf{Name} &
    \textbf{Matric No} &
    \textbf{Score} &
    \textbf{Comments}\\
    \hline
    \endhead

    Wiktor Brodlo &
    s0927919 &
    3&
    I have finished the simulator I was working on and published a document
    explaining how to use the simulator. I have set up the Jenkins continuous
    integration system. I have also contributed to the integration plan and the
    angle system.\\


    David Fraser &
    s0912336 &
    9&
    I continued development of the pure pursuit system and this is now
    producing the arc commands as specified. I also worked on identifying bugs
    in the control system with Dale and I am continuing to work these out of
    the system.\\

    Radoslav Gabrovski &
    s0951580 &
    6& 
    Throughout the past three weeks, I have manly been involved into the
    development of the vision system and I also was involved in the angle
    system and the implementation of some of the control functions for the
    milestone. \\


    James Hulme &
    s0901522 &
    9& 
    This milestone I started off by creating a technique to consistently get
    the robot position accurately. I then polished up multiple areas of the
    vision system providing cleaner and faster code. I also updated the vision
    testing system to keep it up to date with the recent changes.\\

    Dale Myers &
    s0942590 &
    9&
    I shifted my focus away from the vision to the strategy system. Most
    of my time in strategy was spent fixing small bugs, learning how the
    system worked so that I could work independently.  In this respect 
    I was successful as I can pinpoint code and fix
    any errors that come up without bothering others.\\

    Laurie Picken &
    s0903587 &
    6&
    My contributions have been in construction and strategy, I provided a pair
    of prongs at the front of the robot to control the ball whilst dribbling
    and helped to build a kicker that works around the front wheels.  I also
    provided the strategy and command interface for penalty offence and
    defence.\\


    Darie Picu &
    s0935756 &
    6&
    Worked on much of the mathmatics behind the planning system such as ball
    predicition. Also worked on the contruction of the new kicker to go round
    the spinners.\\

    Tomas Tauber &
    s0943263 &
    9&
    I upgraded the LeJOS firmware and library to the new version, wrote an
    initial odometry-based fallback navigation to the initial position,
    stress-tested the whole system and measured its lead using the YourKit
    profiler, and prepared a solution for the milestone with some parts of the
    existing strategy code.\\

    Christopher Williams &
    s0955088 &
    9&
    I have been working on the Planning and Strategy of the robot. This
    includes working on the A* path finding and developing the ”vehicle” that
    creates and carries a plan to the Control Interface of the robot. \\


\end{longtable}
\textbf{Good things} - Improvements to the kicker were made do it can now kick
with the spinners on the front of the robot. Team communication has improved
since the last milestone. Strategy is continuing to progress well.

\textbf{Things to improve} - The control system has been identified as a weak
point for bugs. This should be reworked over the next week or so to remove any
of the bugs and difficulties we encountered over the past few weeks.

\textbf{Goals for next Milestone} - We want to get arcing working properly and
using it move the robot rather than hacked together solutions at the last
minute. Progression in the vision system with barrel distortion and paralleling
would also be ideal.
\end{document}
