\section{Conclusion}

In summary; Our Vision system is stable and fast, running at 25fps, however
time could have been saved by adapting a different code base. Our Strategy
system has scope for further features, but needs a better A*,some simulator for
testing and we would recommend a PID controller for the Control Interface. The
Control code works, but we would suggest changing to a Behaviour Model for
future designs. Our spinners are are a good feature as they provide better ball
control we would highly recommend taking a previous year's robot design as
a start for construction. Our biggest failing was integration of the
sub-systems, as our robot does not behave as designed. 

Due to the delay between Vision creating and updating the \texttt{WorldState} and
Control sending the command to the robot we have created a situation where the
commands issued to the robot are not correct for the current point in time.
More resources should have been allocated into integration of the
subsystems earlier on. Taking a full project from a previous year and
implementing new designs on this would have saved us considerable time, which
could have been spent improving a design.

Our team manager was also writing our Control Interface, this over stretched
one person over two roles. The team manager should not be responsible for
significant code generation. Furthermore we believe that we needed a Technical
Lead, who would have overseen our Integration and kept the project design
technically uniform.
