\section{Control}
%Tom
In the last year's code repository, several teams reported their
Control/Communication sub-system had occasional problems. Group five, however,
did not mention any such problems; their Control code was easy to follow
(clearly defined communication interface and integer operation codes for
controlling the robot) and used leJOS, an actively developed firmware and
framework for LEGO Mindstorms in Java. For these reasons, we based our Control
sub-system on their code.  Using the class \texttt{OdometryPoseProvider}, a
simple fallback navigation was made. It saved the robot's initial position, in
front of our goal, and would move the robot directly there in the event of a
lost bluetooth connection.
%---
\subsection{Final Version}

As stated, our system worked by generating plans as quickly as possible and
sending the instructions to the robot. We discovered however, that the robot
was acting unpredictably with sent commands. The issue was narrowed down to
bluetooth buffering.  It was impossible to see what command the robot was
currently executing. 

The design was changed so the commands were not sent until the previous one was
acknowledged.  This ensured transparency into which commands were being
executed, and thus gave predictability in the robot's actions. Due to Java
limitations it was not possible to send negative numbers. Previous years solved
this problem by adding a large number  to the argument before sending, then
subtracting from the argument at the other end.  A more elegant solution was to
have two different opcodes. A positive direction action and a negative
direction action so that the numbers being sent were always positive.
Furthermore, a new kicking method was introduced. Instead of an explicit and
separate command to kick, an kick flag was put inside each instruction allowing
a kick action and a move action. 

\subsection{Bluetooth measurements}

%Wiktor
In order to further investigate the bluetooth issues, a ping tool was created
to measure the latencies of the protocol.  After running the tool a number of
times, a pattern of latencies can be seen. The latencies can be grouped into
three distinct groups: short, medium, and long. This grouping suggests one or
both of the bluetooth implementations (on the computer and/or on the robot)
contain a buffer. When sending a packet, the packet is put in the buffer, but
it is not sent until the buffer fills in, or a clock tick is fired. Because the
tool will not send the next packet until it receives a response, the controller
is forced to wait on the clock. This might be due to the timing requirements of
the bluetooth specification or an implementation quirk in one or both of the
bluetooth controllers, the bluetooth library, or the NXT communications
library.

\subsection{What would we do differently?}
%Tom
All teams that used leJOS last year and most likely even this year designed
their NXT brick code using one of two approaches or their combination:
competing or collaborating threads and event-triggering. Even though it is
valid and working in most cases, it often results in a ``spaghetti code'' and
is not recommended by leJOS, as we later discovered. The recommended design
pattern for autonomous robots is the \textbf{behaviour control
model}\cite{behaviour}. In this model, each robot's task is defined in its own
class that implements the \textsl{Behavior} (sic) interface and it is clear
what each behaviour does and when, and how it can be suppressed. These
behaviours are then passed with fixed priorities to the \textsl{Arbitrator}
class that regulates which behaviour should be active at any time. If more
behaviours want to take control, only the one with the highest priority will
become active and the current one will be suppressed.

There are many advantages of this pattern: behaviours can be easily added,
removed, or separated for testing; anyone familiar with this model can
understand the code (i.e. more likely to get help from the leJOS community); it
is guaranteed that only one behaviour can be in control at any time; behaviours
do not make any assumptions about their priorities, so that priorities can be
changed without reprogramming behaviours. Furthermore, it would then be easier
to integrate the whole system with leJOS framework tools for robotics. These
tools include, for example, the A* search algorithm that we (and many teams)
implemented on our own.  Using a 3$^{\textrm{rd}}$ party API in this scenario
would enforce the same \textbf{consistent world state representation} and
prevent the project from some problems we had due to the fact that people used
different angle systems and units of measure in their algorithms.
%---
