\documentclass[12pt, a4paper]{article} %Defines the document, we are forced to use 12pt
\usepackage[a4paper,landscape]{geometry}
\usepackage{longtable}
\usepackage[cm]{fullpage} %makes the margins more reasonable for a 1 page report


\begin{document}

\textbf{SDP Group 7 Team Preformance Review 1 - \today}

\begin{longtable}{c c c p{18cm}}
    \textbf{Name} &
    \textbf{Matric No} &
    \textbf{Score} &
    \textbf{Comments}\\
    \hline
    \endfirsthead


    \textbf{Name} &
    \textbf{Matric No} &
    \textbf{Score} &
    \textbf{Comments}\\
    \hline
    \endhead

    Wiktor Brodlo &
    s0927919 &
    3&
    Did some construction work and identified potential problem with motors\\

    David Fraser &
    s0912336 &
    6&
    Mainly administration work, setting up issue trackers, etc. Did work on the
    rebuilds of the robot\\

    Radoslav Gabrovski &
    s0951580 &
    9& 
    Worked on both vision and the construction of the robot. Wrote a different
    thresholding technique for the vision system\\

    James Hulme &
    s0901522 &
    6& 
    Refactored much of the old code we used as a base for the vision system.
    Improved the GUI from old system.\\

    Dale Myers &
    s0942590 &
    6&
    Refactored much of the old code from last year we used for vision system. \\

    Laurie Picken &
    s0903587 &
    6&
    Worked on the construction of the robot and has been involved with much of
    the preplanning for strategy\\

    Darie Picu &
    s0935756 &
    6&
    Worked on the robot mainly, participating in the various rebuilds of it.\\

    Tomas Tauber &
    s0943263 &
    9&
    Did major refactoring of both the control and the vision systems. Also
    produced the ant files which we use to build the systems.\\

    Christopher Williams &
    s0955088 &
    6&
    Has been planning for the strategy systems for the upcoming milestones and
    friendly matches\\


\end{longtable}

\textbf{Good things} - The base functionality for the vision system is just
about finished - two weeks ahead of schedule. The main work of the vision
system from now on will be mainly tuning work. A lot of the preplanning for the
strategy is also going ahead with systems starting to get implemented, well
before we need it.

\textbf{Things to improve} - Some lack of interteam communication caused some
problems with the robot being rebuilt. The robot was rebuilt too many times but we
feel that the current build of the robot will not change much from now on due
to what we learned from the previous rebuilds.

\textbf{Goals for next Milestone} - Our goals for the next milestone are to
have have a working strategy system that can or will be close to handling
a match situation including collision avoidance. Vision system should have
a testing system that will allow us to measure its accuracy and make
improvements to it. We hope to have a working simulator in order to test
strategy and avoidance systems.
\end{document}
